### 2020-12-21 ch01_introduction/introduction.tex
Optimized introduction on chapter 3

This thesis is structured as follows: \Cref{ch:02:scientific_background}
introduces the scientific background. This includes relevant literature that is
used as a baseline for this thesis. \Cref{ch:03:esmvaltool} gives an overview
over the contributions made to the \ac{ESMValTool}, an open-source software for
the analysis of \acp{ESM}. These contributions helped improving the routine
evaluation of \acp{ESM} which is useful for the whole scientific community and
lead to co-authorship in four peer-reviewed studies \autocite{Eyring2020,
  Lauer2020, Righi2020, Weigel2020}. \Cref{ch:04:assessment_climate_metrics}
covers the assessment of policy-relevant climate metrics like the \ac{ECS} and
the \ac{TCR} in the latest generation of \acp{ESM}. This work is already
published in two scientific publications \autocite{Bock2020, Meehl2020}. Since
the \ac{ECS} and \ac{TCR} are considerably higher in this new climate model
generation, \cref{ch:05:paper_ecs} describes the assessment of emergent
constraints (a technique to reduce uncertainties in multi-model climate
projections, see \cref{subsec:02:emergent_constraints}) on the \ac{ECS} for
these \acp{ESM}. The contents of this chapter are published in \emph{Earth
  System Dynamics} \autocite{Schlund2020a}. \Cref{ch:06:paper_gpp} focuses on a
new method to reduce uncertainties in gridded multi-model projections of the
future climate with observations based on \ac{ML}. As an example, the method is
applied to the photosynthesis rate at the end of the \nth{21} century, which is
already published in the \emph{Journal of Geophysical Research: Biogeosciences}
\autocite{Schlund2020}. Finally, \cref{ch:07:summary_outlook} provides a
summary of the results of this thesis and gives an outlook of possible future
works.

>>>>

This thesis is structured as follows: \Cref{ch:02:scientific_background}
introduces the scientific background. This includes relevant literature that is
used as a baseline for this thesis. \Cref{ch:03:esmvaltool} gives an overview
over the contributions made to the \ac{ESMValTool}, an open-source software for
the analysis of \acp{ESM}. These contributions helped improving the routine
evaluation of \acp{ESM} which is useful for the entire scientific community and
lead to co-authorship in four peer-reviewed studies \autocite{Eyring2020,
  Lauer2020, Righi2020, Weigel2020}. \Cref{ch:04:assessment_climate_metrics}
covers the assessment of policy-relevant climate metrics like the \ac{ECS} and
the \ac{TCR} in the latest generation of \acp{ESM}. This work is already
published in two scientific publications \autocite{Bock2020, Meehl2020}. Since
the \ac{ECS} and \ac{TCR} are considerably higher in this new climate model
generation, \cref{ch:05:paper_ecs} describes the assessment of emergent
constraints (a technique to reduce uncertainties in multi-model climate
projections, see \cref{subsec:02:emergent_constraints}) on the \ac{ECS} for
these \acp{ESM}. The contents of this chapter are published in \emph{Earth
  System Dynamics} \autocite{Schlund2020a}. \Cref{ch:06:paper_gpp} focuses on a
new method to reduce uncertainties in gridded multi-model projections of the
future climate with observations based on \ac{ML}. As an example, the method is
applied to the photosynthesis rate at the end of the \nth{21} century, which is
already published in the \emph{Journal of Geophysical Research: Biogeosciences}
\autocite{Schlund2020}. Finally, \cref{ch:07:summary_outlook} provides a
summary of the results of this thesis and gives an outlook of possible future
works.

### 2020-12-21 ch03_esmvaltool/esmvaltool.tex
Optimized introduction on chapter 3

In order to answer the research questions of this thesis posed in
\cref{sec:01:research_questions}, a reliable tool to read, process and evaluate
output from climate model simulations is necessary. A valuable software that
fits these criteria is the \ac{ESMValTool}. The \ac{ESMValTool} is an
open-source community diagnostics and performance metrics tool for the routine
evaluation of \ac{ESM} output, which particularly facilitates the analysis of
\ac{CMIP} models (\url{https://www.esmvaltool.org}). For this reason, all
analyses presented in
\cref{ch:04:assessment_climate_metrics,ch:05:paper_ecs,ch:06:paper_gpp} of this
thesis were implemented into the \ac{ESMValTool}. Apart from that, further
substantial contributions to the code base of the \ac{ESMValTool} have been
made, which lead to co-authorship in the four peer-reviewed studies that
provide its scientific documentation \autocite{Eyring2020, Lauer2020,
  Righi2020, Weigel2020}. After a brief overview over the \ac{ESMValTool}'s
structure, this chapter presents all these contributions that are not
documented in other chapters of this thesis.

>>>>

In order to answer the research questions of this thesis posed in
\cref{sec:01:research_questions}, a reliable and efficient tool to read,
process and evaluate output from climate model simulations is necessary. A
valuable software that fits these criteria is the \ac{ESMValTool}. The
\ac{ESMValTool} is an open-source community diagnostics and performance metrics
tool for the routine evaluation of \ac{ESM} output, which notably facilitates
the analysis of \ac{CMIP} models (\url{https://www.esmvaltool.org}). For this
reason, all analyses presented in
\cref{ch:04:assessment_climate_metrics,ch:05:paper_ecs,ch:06:paper_gpp} of this
thesis were implemented into the \ac{ESMValTool}. Apart from that, further
substantial contributions to the code base of the \ac{ESMValTool} have been
made that improve the routine evaluation of climate models, which is beneficial
for the entire scientific community. Moreover, this lead to co-authorship in
the scientific documentation of the \ac{ESMValTool}, which is published in four
peer-reviewed studies \autocite{Eyring2020, Lauer2020, Righi2020, Weigel2020}.
After a brief overview over the \ac{ESMValTool}'s structure, this chapter
presents all these contributions that are not documented in other chapters of
this thesis.
